Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
HI

#download packages
library(devtools)
library(dplyr)
install_github("nealhaddaway/PRISMA2020")

#create df from example csv file
PRISMA <- read.csv("PRISMA.csv")

#set the REDCap IDs
#last REDCap ID in previous version
last_ID_prev <- 1000
#last REDCap ID in current version
last_ID_current <- 5296
#load all records in redcap

# get the data directly from redcap:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='158',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response_all <- httr::POST(url, body = formData, encode = "form")
all_records <- httr::content(response_all)

#find number of studies identified in databases since previous update
current_records <- all_records[last_ID_prev:last_ID_current, ]
PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484

#find number included in review
PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))

#find number of duplicates removed before screening
PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
#find number of records screening
PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
  nrow(current_records %>% filter(ex_reas == 14))
#add number of studies found via other methods 
#1 study #9484 was added manually - it's the published v of a preprint
#as a result, I need to minus 1 record from the database result
PRISMA$n[PRISMA$box == "othstud"] <- 1

#find number of records excluded from title and abstract
PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
check <- current_records %>% filter(ex_reas == 1)
#current records left after title and abstract screening
full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)

#find number of full texts retrieved
PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
  (nrow(current_records %>% filter(ex_reas == 14)) + 
  nrow(current_records %>% filter(ex_reas == 1)))

#find number of full texts screened
PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
  (nrow(current_records %>% filter(ex_reas == 14)) + 
     nrow(current_records %>% filter(ex_reas == 1)))

#find number included in previous version
prev_records <- all_records[1:last_ID_prev, ]
PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])

#calculate total studies included
PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
  nrow(current_records[current_records$review == 1, ])

# studies excluded
excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))

excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
                       "; No original data, ", excl_12, 
                       "; Data included in other publication, ", excl_13, 
                       "; Insufficient extractable data, ", excl_15, 
                       "; Study design inappropriate, ", excl_16, 
                       "; No PCR/serological test, ", excl_17, 
                       "; Math. model not in review scope, ", excl_19, 
                       "; Inadequate follow-up time, ", excl_20, 
                       "; Preprint of published article, ", excl_21, 
                       "; Other, ", excl_18)
excl_reasons
PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons

#fix some text in the flowchart data
PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"

#read data
flowchart <- PRISMA2020::PRISMA_data(PRISMA)
flowchart
#generate flowchart
PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)

PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)

@@

## PRISMA 2020 Flowchart
![Figure 3. PRISMA 2020 Flow Diagram](PRISMA2020_flowdiagram.png)
***

>>>>

#download packages
library(devtools)
library(dplyr)
#install_github("nealhaddaway/PRISMA2020")

#create df from example csv file
#PRISMA <- read.csv("PRISMA.csv")

#set the REDCap IDs
#last REDCap ID in previous version
#last_ID_prev <- 1000
#last REDCap ID in current version
#last_ID_current <- 5296
#load all records in redcap

# get the data directly from redcap:
# url <- "https://redcap.ispm.unibe.ch/api/"
# token <- "F2725F15FE84D2832E2793BB23B0A62B"
# formData <- list("token"=token,
#                  content='report',
#                  format='csv',
#                  report_id='158',
#                  csvDelimiter='',
#                  rawOrLabel='raw',
#                  rawOrLabelHeaders='raw',
#                  exportCheckboxLabel='false',
#                  returnFormat='csv'
# )
# response_all <- httr::POST(url, body = formData, encode = "form")
# all_records <- httr::content(response_all)
# 
# #find number of studies identified in databases since previous update
# current_records <- all_records[last_ID_prev:last_ID_current, ]
# PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484
# 
# #find number included in review
# PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))
# 
# #find number of duplicates removed before screening
# PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
# #find number of records screening
# PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
#   nrow(current_records %>% filter(ex_reas == 14))
# #add number of studies found via other methods 
# #1 study #9484 was added manually - it's the published v of a preprint
# #as a result, I need to minus 1 record from the database result
# PRISMA$n[PRISMA$box == "othstud"] <- 1
# 
# #find number of records excluded from title and abstract
# PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
# check <- current_records %>% filter(ex_reas == 1)
# #current records left after title and abstract screening
# full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)
# 
# #find number of full texts retrieved
# PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
#   (nrow(current_records %>% filter(ex_reas == 14)) + 
#   nrow(current_records %>% filter(ex_reas == 1)))
# 
# #find number of full texts screened
# PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
#   (nrow(current_records %>% filter(ex_reas == 14)) + 
#      nrow(current_records %>% filter(ex_reas == 1)))
# 
# #find number included in previous version
# prev_records <- all_records[1:last_ID_prev, ]
# PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])
# 
# #calculate total studies included
# PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
#   nrow(current_records[current_records$review == 1, ])
# 
# # studies excluded
# excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
# excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
# excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
# excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
# excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
# excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
# excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
# excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
# excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
# excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))
# 
# excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
#                        "; No original data, ", excl_12, 
#                        "; Data included in other publication, ", excl_13, 
#                        "; Insufficient extractable data, ", excl_15, 
#                        "; Study design inappropriate, ", excl_16, 
#                        "; No PCR/serological test, ", excl_17, 
#                        "; Math. model not in review scope, ", excl_19, 
#                        "; Inadequate follow-up time, ", excl_20, 
#                        "; Preprint of published article, ", excl_21, 
#                        "; Other, ", excl_18)
# excl_reasons
# PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons
# 
# #fix some text in the flowchart data
# PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
# PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"
# 
#   
# #read data
# flowchart <- PRISMA2020::PRISMA_data(PRISMA)
# flowchart
# #generate flowchart
# PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
# flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
#                                
# PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)

#######ROB Analysis HI##########

@@

## PRISMA 2020 Flowchart
*In progress.*
***
